A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-02-17 paper/paper.tex
Added commas to 4-digit numbers

\paragraph{Unlabelled, undirected}
\cref{figure:plain-cumulative} shows a plot of cumulative run times (x-axis)
against number of problem instances solved (y-axis).  We may compare
the speed of two algorithms using the horizontal distance between their curves.
For example, we could solve 2000 of the 4110 unlabelled undirected instances
using the \McSplit\ algorithm if a time limit of 0.5 seconds per instance were
imposed.  Its nearest competitor, CP-FC, would require a time limit of over 24
seconds per instance to solve the same number of instances.  For any given
number of instances, \McSplit\ is comfortably more than an order of magnitude
faster than its nearer competitor  Moreover, there are few instances in this
set for which \McSplit\ is not the fastest solver; of the 3506 instances that
could be solved by at least one of \McSplit, $k\downarrow$, CP-FC and clique in less than than
1000 seconds, there were 426 instances on which \McSplit\ was not strictly
faster than the other two solvers.

@@

\paragraph{Large subgraph isomorphism instances} We also ran the algorithms on
a set of 5725 larger instances used in recent studies of subgraph
isomorphism~\citep{DBLP:conf/lion/KotthoffMS16} and maximum common
subgraph~\citep{UpcomingAAAIPaper}.  This benchmark set includes real-world
graphs and graphs generated using random models.  Pattern graphs range from 4
vertices to 900 with a median of 80; target graphs range from 10 vertices to
6671 with a median of 561. Cumulative runtimes on these instances are shown in
\cref{figure:sip-cumulative}.  This is a challenging set of instances, and more
than half of the instances cannot be solved within a timeout of 1000 seconds by
any solver. Furthermore, the CP-FC algorithm and the clique encoding run out of
memory on many of the instances (these are treated as timeouts).

>>>>

\paragraph{Unlabelled, undirected}
\cref{figure:plain-cumulative} shows a plot of cumulative run times (x-axis)
against number of problem instances solved (y-axis).  We may compare
the speed of two algorithms using the horizontal distance between their curves.
For example, we could solve 2,000 of the 4,110 unlabelled undirected instances
using the \McSplit\ algorithm if a time limit of 0.5 seconds per instance were
imposed.  Its nearest competitor, CP-FC, would require a time limit of over 24
seconds per instance to solve the same number of instances.  For any given
number of instances, \McSplit\ is comfortably more than an order of magnitude
faster than its nearer competitor  Moreover, there are few instances in this
set for which \McSplit\ is not the fastest solver; of the 3,506 instances that
could be solved by at least one of \McSplit, $k\downarrow$, CP-FC and clique in less than than
1,000 seconds, there were 426 instances on which \McSplit\ was not strictly
faster than the other two solvers.

@@

\paragraph{Large subgraph isomorphism instances} We also ran the algorithms on
a set of 5,725 larger instances used in recent studies of subgraph
isomorphism~\citep{DBLP:conf/lion/KotthoffMS16} and maximum common
subgraph~\citep{UpcomingAAAIPaper}.  This benchmark set includes real-world
graphs and graphs generated using random models.  Pattern graphs range from 4
vertices to 900 with a median of 80; target graphs range from 10 vertices to
6,671 with a median of 561. Cumulative runtimes on these instances are shown in
\cref{figure:sip-cumulative}.  This is a challenging set of instances, and more
than half of the instances cannot be solved within a timeout of 1,000 seconds by
any solver. Furthermore, the CP-FC algorithm and the clique encoding run out of
memory on many of the instances (these are treated as timeouts).
